---
title: "Additional Tables and Analyses"
---

This page contains additional tables and statistical analyses that complement the main results in the paper.
```{r}
#| echo: false
#| warning: false
#| message: false

# Load required packages
library(DT)
library(arrow)

# Source the table functions
source("R/02-TableFunctions.R")
```

---

## Term Lists

Our analysis examines accounting terminology across different datasets. Below are the complete term lists used in our study.

### Dataset Overview

We analyze three distinct corpora:

- **10-K Reports** (~50,000 U.S. annual reports)
- **20-F Reports** (International filers in the U.S.)
- **Rest of World** (Non-U.S. reports from various jurisdictions)

Each table shows the terms (n-grams) identified, along with their unique term IDs and the specific n-gram length.

---

::: {.panel-tabset}

## Top-Down Termlist

**Top-Down Termlist**
```{r}
#| echo: false
#| warning: false
#| message: false

create_interactive_table(
  .data = arrow::read_parquet("data/Termlists/TermListROW.parquet"),
  .page_length = 10L,
  .column_align = c("center", "center", "left"),
  .header_align = "center",
  .filter = "none",
  .font_size = 14L,
  .row_padding = 2L
)  
```

## Bottom-Up (10-K)

**U.S. domestic filers (Form 10-K)**
```{r}
#| echo: false
#| warning: false
#| message: false

create_interactive_table(
  .data = arrow::read_parquet("data/Termlists/TermList10K.parquet"),
  .page_length = 10L,
  .column_align = c("center", "center", "left"),
  .header_align = "center",
  .filter = "none",
  .font_size = 14L,
  .row_padding = 2L
)
```

## Bottom-Up (20-F)

**International filers in the U.S. (Form 20-F)**
```{r}
#| echo: false
#| warning: false
#| message: false

create_interactive_table(
  .data = arrow::read_parquet("data/Termlists/TermList20F.parquet"),
  .page_length = 10L,
  .column_align = c("center", "center", "left"),
  .header_align = "center",
  .filter = "none",
  .font_size = 14L,
  .row_padding = 2L
)
```

:::

---

## Download

**Download all term lists in a formatted Excel file (with separate sheets for each dataset):**

📥 [Download Term Lists (Excel, 2.6 MB)](downloads/Termlists.xlsx)

---

## Notes

- **TID**: Term ID - unique identifier for each term
- **nGram**: Length of the term (number of words)
- **Term**: The actual accounting term or phrase