---
title: "Robustness Checks"
---

This page presents robustness checks and alternative specifications for our main results.

---

## Robustness Check 1: [Title]

**Description:** Brief description of this robustness check and what it tests.
```{r}
#| echo: false
#| warning: false

# Your regression code here
# Example using modelsummary:
# library(modelsummary)
# models <- list(
#   "Model 1" = lm(y ~ x1 + x2, data = your_data),
#   "Model 2" = lm(y ~ x1 + x2 + x3, data = your_data)
# )
# modelsummary(models, stars = TRUE)
```

**Interpretation:** What do these results tell us?

---

## Robustness Check 2: [Title]

**Description:** Brief description of this robustness check.
```{r}
#| echo: false
#| warning: false

# Your regression code here
```

**Interpretation:** What do these results tell us?

---

## Alternative Specification: [Title]

**Description:** Description of the alternative specification.
```{r}
#| echo: false
#| warning: false

# Your code here
```

**Interpretation:** What do these results tell us?

---

## Summary

Brief summary of what the robustness checks collectively show and how they support the main findings.